\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2019-05-24 ms.tex
a few minor tweaks

\changes{The instrumental photometry (i.e., $-2.5\log(\textrm{ADU}~\textrm{sec}^{-1}$) was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and with SkyMapper \citep{Wolf:2018} for the u-band observations.
We use a robust linear fit to cross-matched sources (that appear in both PS1 and our observations) to obtain a zero-point and color-term (no color-term was used for the u-band) to derive color transformations relating our instrumental DECam photometry to calibrated PS1 grizy and SkyMapper u-band photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
We apply this color transformation to the instrumental photometry to put our photometry on the PS1/DECam system. % ---including a constant 25 mag offset applied by DAOPHOT and an offset by $2.5\,\log{t_{\rm exp}}$ given the exposure time $t_{\rm exp}$---
This calibration enables us to treat the photometry as if it were PS1 (g- and i-band) and DECam (u-band) photometry in the isochrone modeling described below.
The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
The larger scatter in u-band---larger than the uncertainty in the individual photometry---is due to the significant differences between the DECam and SkyMapper u-band passbands as well as the u-band's sensitivity to both temperature and metallicity. 
}

>>>>

\changes{The instrumental photometry (i.e., $-2.5\log(\textrm{ADU}~\textrm{sec}^{-1}$) was calibrated using Pan-STARRS1 \citep[PS1;][]{Chambers:2016} photometry for g- and i-band and with SkyMapper \citep{Wolf:2018} for the u-band observations.
We use a robust linear fit to cross-matched sources (that appear in both PS1/SkyMapper and our observations) to obtain a zero-point and (for g- and i-band) color-term to derive color transformations relating our instrumental DECam photometry to calibrated PS1 grizy and SkyMapper u-band photometry (see \tablename~\ref{tbl:transphot} for the derived transformation coefficients).
We apply this color transformation to the instrumental photometry to put our photometry on the PS1/DECam system. % ---including a constant 25 mag offset applied by DAOPHOT and an offset by $2.5\,\log{t_{\rm exp}}$ given the exposure time $t_{\rm exp}$---
This calibration enables us to treat the photometry as if it were PS1 (g- and i-band) and DECam (u-band) photometry in the isochrone modeling described below.
The robust RMS around the linear fit is 0.028 mag for g- and i-band and 0.164 mag for the u-band; We adopt these RMS values as systematic errors that are added in quadrature to the photometric uncertainties for individual sources in the modeling described below.
The larger scatter in u-band---larger than the uncertainty in the individual photometric measurements---is due to the significant differences between the DECam and SkyMapper u-band passbands as well as the u-band's sensitivity to both temperature and metallicity.
}
